Moisture effects on leaf litter are species-specific and result in non-additive flammability in mixed conifer forest

### 2019-08-06 ms/Magalhaes_Schwilk_litter_flam_moisture.tex
Move citations to shorter custom bib file
Other minor corrections

\begin{document}

\maketitle

@@

% . The moisture content of a mixture at any given time was also dependent upon the bulk density of the mixture (anova analysis resulted in a better model if bulk density was included as a fixed effect, p=0.01135).

@@

\section*{Author contributions}
  conceptualization, RMQM and DWS; methodology, RMQM and
  DWS; experiments, RMQM; coding and data analysis, DWS and RMQM; writing DWS
  and RMQM; writing--review and editing, DWS

@@

\newpage
\bibliography{/home/schwilk/write/bib/schwilk}

>>>>

\begin{document}
\maketitle

@@

@@

\section*{Author contributions}

conceptualization, RMQM and DWS; methodology, RMQM and DWS; experiments, RMQM;
coding and data analysis, DWS and RMQM; writing DWS and RMQM; writing--review
and editing, DWS

@@

\newpage
\bibliography{Magalhaes_Schwilk_litter_flam_moisture.bib}
